Blum axioms and nondeterministic computation of functions

### 2016-04-20 paper.tex
paper.tex: Remove some padding in Krentel's and Valiant's section.

Therefore, Krentel's $\OptP$ class contains the optimization problems
that can be ``solved'' in polynomial time by nondeterministic Turing machines.
(Note we must always take the maximum value, or always take the minimum value.
We could associate a Gödel numbering by, say,
adding one bit to the machine encoding.
And, by the same reasoning we made in our definition,
the corresponding complexity measure satisfy Blum axioms.)

The definition of $\OptP$-completeness, however,
is significantly different.

@@

Valiant takes a different approach to defining how to extract a value
from the set of strings written by all branches of a computation:
just count the number of accepting branches.

\begin{definition}[Valiant's definition]
    A nondeterministic machine $M$ computes a function $f: \{0, 1\}^* \to \mathbb N$ if,
    for every input $x$,
    $M$ halts on every branch\footnote{
        Valiant did not include the requirement of halting in his definition,
        but we will include it to avoid having the same problems
        of Hopcroft and Ullman's definition.
    }
    and the number of accepting branches of computation is $f(x)$
    \cite[p.~191]{Valiant1979}.
\end{definition}
This approach also yields acceptable Gödel numberings and Blum complexity measures.

@@

Since there are reductions of the Boolean satisfiability problem
that preserves the number of accepting paths\footnote{
    Such reductions are called \emph{parsimonious} \cite[p~346]{AroraBarak2009}.
},
the problem of counting the number of satisfying assignments is $\#\P$-complete.
Valiant also proves less trivial problems are $\#\P$-complete,
like the task of computing the permanent of a matrix,
even when the matrix is restricted to have only $0$ and $1$ as entries
\cite[p.~194]{Valiant1979}.
Therefore,
this definition is also flexible, like Krentel's.

>>>>

Therefore, Krentel's $\OptP$ class contains the optimization problems
that can be ``solved'' in polynomial time by nondeterministic Turing machines.
(Note we must always take the maximum value, or always take the minimum value.)
The definition of $\OptP$-completeness, however,
is significantly different.

@@

\begin{definition}[Valiant's definition]
    A nondeterministic machine $M$ computes a function $f: \{0, 1\}^* \to \mathbb N$ if,
    for every input $x$,
    $M$ halts on every branch\footnote{
        Valiant did not include the requirement of halting in his definition,
        but we will include it to avoid having the same problems
        of Hopcroft and Ullman's definition.
    }
    and the number of accepting branches of computation is $f(x)$
    \cite[p.~191]{Valiant1979}.
\end{definition}

@@

Besides problems like counting the number of satisfying assignments
for a given formula,
Valiant also proves less trivial problems are $\#\P$-complete,
like the task of computing the permanent of a matrix
\cite[p.~194]{Valiant1979}.
Therefore,
this definition is also flexible, like Krentel's.
